%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research Appointments}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Postdoctoral Fellow in Shirlee Wohl's lab} % Job title
    {Brigham and Women's Hospital at Harvard Medical School} % Organization
    {Boston, Massachusetts} % Location
    {Summer 2023-Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Investigated the epidemiological and genetic factors that enable intermittent outbreaks of Vibrio Cholerae in Africa.}
        \item {Designed and assessed sequencing library preparation methods for a variety of Cholera sample collection techniques.}
        \item {Conducted sequencing and bioinformatic workshops in Africa to advance the genomic surveillance capacity in the region.}
        \item {Developed bioinformatics pipeline to enable rapid assembly and analysis of Vibrio Cholerae whole genome sequencing data.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Graduate Student in Kristian Andersen's lab} % Job title
    {The Scripps Research Institute} % Organization
    {La Jolla, California} % Location
    {Spring 2018-Summer 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Utilized abundant SARS-CoV-2 genomic surveillance data to investigate temporal dynamics in the connectedness of local epidemics, factors driving bidirectional transmission, and the effectiveness of international travel restrictions.}
        \item {Developed and maintained publicly available dashboards reflecting clinical and wastewater surveillance of SARS-CoV-2 in San Diego County and Baja California (16K+ views; https://searchcovid.info/Dashboards/).}
        \item {Investigated the genetic, host, and environmental factors that enable intermittent outbreaks of West Nile virus in the Americas to better inform viral monitoring and control.}
        \item {Developed and optimized method to measure intra-batch contamination in multiplexed amplicon-based sequencing library preparation.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {REU Internship in Joaquin Martinez's lab} % Job title
    {Bigelow Laboratory for Ocean Sciences} % Organization
    {Boothbay, Maine} % Location
    {Summer 2016} % Date(s)
    {
      \begin{cvitems}
        \item{Studied the effect of climate change on the abundance of highly prevalent and significant marine viruses.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Assistant in Line Cui's lab} % Job title
    {University of New Mexico} % Organization
    {Albuquerque, New Mexico} % Location
    {Fall 2015-Spring 2017} % Date(s)
    {
      \begin{cvitems}
        \item{Studied how trafficking of heparanase influences cancer metastasis.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
