%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Presentations}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
 \begin{cventries}
  \cventry
    {\textbf{Workshop}: Phylogenetic analysis of \textit{Vibrio cholerae} in the cloud.} % Role
    {CholGEN Workshop} % Event
    {Addis Ababa, Ethiopia} % Location
    {Feb. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Instructed participants how on to perform de novo assembly and phylogenetic reconstruction on \textit{Vibrio cholerae} genomes using Terra.}
      \end{cvitems}
    }
  
  \cventry
     {\textbf{Workshop}: Whole genome sequencing and analysis of \textit{Vibrio cholerae}} % Role
    {CholGEN Workshop} % Event
    {Kinshasa, DRC} % Location
    {Sep. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s)
      \item {Introduced a general python workflow to assemble and analyze \textit{Vibrio cholerae} genomes.}
      \end{cvitems}
    }


  \cventry
    {\textbf{Talk}: Genomic surveillance reveals highly connected COVID-19 epidemics} % Role
    {SEARCH Alliance Meeting} % Event
    {La Jolla, CA} % Location
    {Oct. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item{Presented project investigating the effectiveness of US-Mexico border closure on transmission between San Diego and Baja California.}
      \end{cvitems}
    }
    
  \cventry
    {\textbf{Poster}: The WestNile4K Project} % Role
    {MVCAC Annual Conference} % Event
    {San Diego, CA} % Location
    {Jan. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Described the goal and achievements of the project in order to engage collaborators within vector control.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\textbf{Workshop}: Identification and Charaterization of T cell Subsets from Single Cell Data} % Role
    {CViSB Annual Workshop} % Event
    {San Diego, CA} % Location
    {Feb. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Introduced a general python workflow to analyze single cell RNA-seq data derived from peripheral blood mononuclear cells.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\textbf{Talk}: The effect of increasing temperature and CO2 levels on the abundance of key marine viruses} % Role
    {ASLO Aquatic Sciences Meeting} % Event
    {Honolulu, HI} % Location
    {Feb. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Described culmination of summer research internship on the impact of global warming and ocean acidifcation.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
